---
title: "Week_4_Exercises"
author: "Shannon Cheng"
date: "5/28/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(nycflights13)
```

# 7.3.4 Exercises

### 1. Explore the distribution of each of the ```x```, ```y```, and ```z``` variables in ```diamonds```. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

``` {r}
ggplot(data = diamonds) +
  geom_freqpoly(binwidth=0.1,aes(x = x), color = "red") +
  geom_freqpoly(binwidth=0.1,aes(x = y), color = "blue") +
  geom_freqpoly(binwidth=0.1,aes(x = z), color  ="green") 
```

### 2. Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)

```{r}
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(data = diamonds, aes(x = price))
```

### 3. How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?

```{r}
filter(diamonds,carat==0.99) %>% count()
```

```{r}
filter(diamonds,carat==1) %>% count()
```

### 4. Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?

```{r}
diamonds %>% 
  ggplot() +
  geom_histogram(aes(x = carat))
```

```{r}
diamonds %>% 
  ggplot() +
  geom_histogram( aes( x = carat ) ) +
  coord_cartesian(ylim=c(0,15000))
```

```{r}
diamonds %>% 
  ggplot() +
  geom_histogram( aes( x = carat ) ) +
  ylim( c(0,7500) )
```


# 7.4.1 Exercises

### 1. What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?

The missing values are removed from the charts.


### 2. What does ```na.rm = TRUE``` do in ```mean()``` and ```sum()```?

It removes ``na`` values while calculating mean and sum.


# 7.5.1.1 Exercises

### 1. Use what you’ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights.

```{r}
library(nycflights13)
```

```{r}
nycflights13::flights %>%
  mutate(
    cancelled=is.na(dep_time),
    sched_hour=sched_dep_time %/% 100,
    sched_min=sched_dep_time %% 100,
    sched_dep_time=sched_hour + sched_min / 60
  ) %>%
  ggplot() +
  geom_boxplot(mapping=aes(y=sched_dep_time, x=cancelled))
```


### 2. What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?

```{r}
ggplot(data=diamonds)+
  geom_violin(mapping=aes(x=cut, y=price))
```

```{r}
ggplot(data=diamonds)+
  geom_point(mapping=aes(x=carat, y=price), alpha=0.4)+
  facet_wrap(~clarity)
```

### 3.Install the ggstance package, and create a horizontal boxplot. How does this compare to using ```coord_flip()```?

``` {r}
library(ggstance)

nycflights13::flights %>%
  mutate(
    cancelled=is.na(dep_time),
    sched_hour=sched_dep_time %/% 100,
    sched_min=sched_dep_time %% 100,
    sched_dep_time=sched_hour + sched_min / 60
  ) %>%
ggplot()+
  geom_boxploth(mapping=aes(y=cancelled, x=sched_dep_time))
```

```{r}
nycflights13::flights %>%
  mutate(
    cancelled=is.na(dep_time),
    sched_hour=sched_dep_time %/% 100,
    sched_min=sched_dep_time %% 100,
    sched_dep_time=sched_hour + sched_min / 60
  ) %>%
  ggplot()+
  geom_boxplot(mapping=aes(y=sched_dep_time, x=cancelled))+
  coord_flip()
```


### 5.Compare and contrast ```geom_violin()``` with a facetted ```geom_histogram()```, or a coloured ```geom_freqpoly()```. What are the pros and cons of each method?

```{r}
nycflights13::flights %>%
  mutate(
    cancelled=is.na(dep_time),
    sched_hour=sched_dep_time %/% 100,
    sched_min=sched_dep_time %% 100,
    sched_dep_time=sched_hour + sched_min / 60
  ) %>%
ggplot()+
  geom_violin(mapping=aes(x=carrier,y=dep_time))
```

```{r}
ggplot(data=diamonds)+
  geom_violin(mapping=aes(x=cut, y=carat))
```

```{r}
ggplot(data=diamonds)+
  geom_histogram(mapping=aes(x=carat))+
  facet_wrap(~cut)
```

```{r}
ggplot(data=diamonds)+
  geom_boxplot(mapping=aes(x=cut, y=carat))
```

### 6.If you have a small dataset, it’s sometimes useful to use ```geom_jitter()``` to see the relationship between a continuous and categorical variable. The ggbeeswarm package provides a number of methods similar to ```geom_jitter()```. List them and briefly describe what each one does.


```{r}
ggplot(data=diamonds)+
  geom_jitter(mapping=aes(x=cut, y=carat), alpha=0.4, dodge.width=0.8)
```

# 7.5.2 Exercises

### Describe an experiment that would have 2 categorical variables.

##### Arabidopsis seed packet families vs. existence of luciferase promoter.


# 7.5.3 Exercises

### Describe an experiment that would have 2 continuous variables.

##### Arabidopsis hypocotyl length vs. days since germination.







