---
title: "Week_3_Exercises"
author: "Shannon Cheng"
date: "5/28/2020"
output: 
  html_document: 
    keep_md: yes
---

# 4.4 Exercises

### 1. Why does this code not work?
```{r}
my_variable <- 10
my_variable
```

### 2. Tweak each of the following R commands so that they run correctly:
```
library(tidyverse)

ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

```{r}
filter(mpg, cyl == 8)
```

```{r}
filter(diamonds, carat > 3)
```

### 3. Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

##### Tools.


# 5.2..4 Exercises

### 1. Find all flights that

#### 1. Had an arrival delay of two or more hours

##### 
```{r}
library(nycflights13)
library(tidyverse)
filter(flights, arr_delay == 120)
```

#### 2. Flew to Houston (IAH or HOU)

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, dest == 'HOU' | dest == 'IAH')
```

#### 3. Were operated by United, American, or Delta

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, carrier == 'UA' | carrier == 'AA' | carrier == 'DA')
```

#### 4. Departed in summer (July, August, and September)

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, month == 7 | month == 8 | month == 9)
```

#### 5. Arrived more than two hours late, but didn’t leave late

```{r}
library(nycflights13)
library(tidyverse)
filter(flights,arr_delay > 120, dep_delay <= 0)
```

#### 6. Were delayed by at least an hour, but made up over 30 minutes in flight

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, dep_delay > 60, air_time > 30)
```

#### 7. Departed between midnight and 6am (inclusive)

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, hour >= 0, hour <= 6)
```

### 2. Another useful dplyr filtering helper is ```between()```. What does it do? Can you use it to simplify the code needed to answer the previous challenges?

##### Between codes for an inclusive range of data. An example of how to use it is ```filter( flights, between(dep_time, 0, 6))```

### 3. How many flights have a missing ```dep_time```? What other variables are missing? What might these rows represent?

```{r}
library(nycflights13)
library(tidyverse)
filter(flights, is.na(dep_time) )
```


# 5.3.1 Exercises

### 1. How could you use ```arrange()``` to sort all missing values to the start? (Hint: use is.na()).

```{r}
library(nycflights13)
library(tidyverse)
arrange(flights, desc(is.na(dep_time)), dep_time)
```

### 2. Sort ```flights``` to find the most delayed flights. Find the flights that left earliest.

```{r}
library(nycflights13)
library(tidyverse)
arrange(flights, desc(dep_delay)) 
```

```{r}
library(nycflights13)
library(tidyverse)
arrange(flights, dep_time)
```

### 4. Which flights travelled the farthest? Which travelled the shortest?

```{r}
library(nycflights13)
library(tidyverse)
arrange(flights, desc(distance))
```

```{r}
library(nycflights13)
library(tidyverse)
arrange(flights, distance)
```


# 5.4.1 Exercises

### 1. Brainstorm as many ways as possible to select ```dep_time```, ```dep_delay```, ```arr_time```, and ```arr_delay``` from flights.

### 2. What happens if you include the name of a variable multiple times in a ```select()``` call?

```{r}
library(nycflights13)
library(tidyverse)
select(flights, distance, distance)
```

##### It doesn't do anything further from the first (repeated) variable.

### 3. What does the ```one_of()``` function do? Why might it be helpful in conjunction with this vector?

```vars <- c("year", "month", "day", "dep_delay", "arr_delay")```

##### It would make a table with the variables year, month, day, dep_delay, and arr_delay.

### 4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

```select(flights, contains("TIME"))```

##### Case is not sensitive to capitlization.


# 5.5.2 Exercises

### 1. Currently ```dep_time``` and ```sched_dep_time``` are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
library(nycflights13)
library(tidyverse)
transmute(flights,
  dep_time_since_midnight = (dep_time %% 100) + ((dep_time %/% 100) * 60),
  sched_dep_time_since_midnight = (sched_dep_time %% 100) + ((sched_dep_time %/% 100) * 60))
```

### 2. Compare ```air_time``` with ```arr_time - dep_time```. What do you expect to see? What do you see? What do you need to do to fix it?

##### Air time should be the same as arr_time - dep_time. However, the units are not the same, so it does not match. To fix this, we need to recode to 

```{r}
transmute(flights,
          air_time,
          arr_minutes = (arr_time %% 100) + ((arr_time %/% 100) * 60),
          dep_minutes = (dep_time %% 100) + ((dep_time %/% 100) * 60),
          arr_dep_minutes_diff = arr_minutes - dep_minutes
          )
```

### 3. Compare ```dep_time```, ````sched_dep_time```, and ```dep_delay```. How would you expect those three numbers to be related?

##### ```dep_delay``` = ```dep_time - sched_dep_time```

### 4. Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for ```min_rank()```.

```{r}
mutate(flights,
dep_delay_rank = min_rank(-dep_delay))%>%
arrange(dep_delay_rank)
```

### 5. What does ```1:3 + 1:10``` return? Why?


# 5.6.7 Exercises

### 5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about ```flights %>% group_by(carrier, dest) %>% summarise(n())```)






